### 2017-10-15 Draft2.tex
Big-P complexity of adding for funnel array impl

	Let $k$ be the number of times the tail is added to. Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$. Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$. Then the formula for $\nwritesresizefn(n)$ is

@@

	Now I wish to find the number of writes [resize] performs.

	\begin{align*}
	\nwritesnewfn(\varnitems) = \biggo(\varnitems)
	\end{align*}

@@

	\begin{align*}
	\end{align*}

>>>>

	Let $k$ be the number of times the tail is added to. Since the tail is a dynamic array, the number of writes it makes is $\nwritesfn(k)$. Since we call [resize] $|S_R|$ times and it adds to the tail each time except for the first, $k = |S_R| - 1 = \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil$. Then the formula for $\nwritesresizefn(n)$ is

@@

	I now approximate this expression with big-P notation. First, I establish an approximation for $k$ using big-O:

	\begin{align*}
	k &= \lceil \log_{\growthfactornew} \varnitems - \log_{\growthfactornew} \initcapacitynew \rceil\\
	\bigo(k) &= \bigo(\log \varnitems)
	\end{align*}

	Then, it is shown that the $k$-term disappears when analyzing the big-P complexity of $\nwritesnewfn(\varnitems)$, leaving just $\biggo(\varnitems)$:

	\begin{align*}
	\biggo(\nwritesnewfn(\varnitems)) &= \biggo(\varnitems + \nwritesfn(k))\\
	&= \biggo(\varnitems) + \biggo(\nwritesfn(k))\\
	&= \biggo(\varnitems) + \bigo(\log \varnitems)\\
	&= \biggo(\varnitems)
	\end{align*}

@@
